---
title: "Control Charts A4_ Q3- Thiwanka Jayasiri"
output: html_notebook
---



1 - Load the required libraries.

2 - Aggregate the data by the year-month-date( for this we require library - Lubridate).

3 - Can use library skimr for the quick statsitical overview and to get an idea of the missing values.

4 - Once we trim the  Time stamp as to  YYYY-MM-DD format we can use it group by and then plot the required control charts - 'xbar', 's' and 'run'.

5 - A quick overview of the chart types are as follows:

  Xbar and S charts for average measurements : If there is more than one measurement in each subgroup the Xbar and S charts will display the average and                                                      the within subgroup standard deviation respectively.
  
  Run charts: run charts (using appropriate rules) are more sensitive to moderate, persistent shifts in data (< 2 SD) than control charts



```{r}
library(qicharts2)
library(caret)
library(skimr)

library(readr)
library(dplyr)
library(lubridate)
```


```{r}
newdf <- read.csv('C:\\Users\\DELL\\Desktop\\Desktop Work\\Data423\\ASS4\\monitor.csv')

# newdf %>% 
#   mutate(hour_of_day = as.date(as.POSIXct(datetime(newdf, "%m/%d/%Y %H:%M:%S")))) %>% 
#   group_by(hour_of_day)

head(newdf)
str(newdf)

```



Its requires to be aggregated using date , hence we need to extract the date only from Timesteamp coloum and crate a new data frame to proceeed with the rest


```{r}

mydate <- as.Date(newdf$Timestam)
head(mydate)

```


```{r}
Process_Memory <- newdf$ProcessMemory
Prediction <- newdf$Prediction
prediction_timems <- newdf$PredictionTimeMS

data <- data.frame(mydate,Process_Memory,Prediction,prediction_timems)
head(data)
summary(data)
str(data)
```

```{r}
aggregate(prediction_timems~ mydate, data =df , mean)
```


#ProcessMemory - the allocated memory (MB) of the relevant server process

Is the memory usage of the server in control? "NO" , It's out of control and by observing the 'X-bar' we can notice that the chart lines goes beyond the upper control limits. 

ProcessMemory - the allocated memory (MB) of the relevant server process

#Process Memory - Xbar Chart

```{r}

qicharts2::qic(x = mydate, y = Process_Memory, data = data, chart = "xbar", subtitle = "Process Memomry" , xlab = "Month" , ylab = "Allocated server process(MB)")


summary(qicharts2::qic(x = mydate, y = Process_Memory, data = data, chart = "xbar", subtitle = "Process Memomry" , xlab = "Month" , ylab = "Allocated server process(MB)"))

qicharts2::qic(x = mydate, y = Process_Memory, data = data, chart = "xbar", subtitle = "Process Memomry" ,freeze = 20, xlab = "Month" , ylab = "Allocated server process(MB)")

summary(qicharts2::qic(x = mydate, y = Process_Memory, data = data, chart = "xbar", subtitle = "Process Memomry" ,freeze = 20, xlab = "Month" , ylab = "Allocated server process(MB)"))


```

#Process Memory - S chart 


```{r}
qicharts2::qic(x = mydate, y = Process_Memory, data = data, chart = "s", subtitle = "Process Memomry", xlab = "Month" , ylab = "Allocated server process(MB)")

summary(qicharts2::qic(x = mydate, y = Process_Memory, data = data, chart = "s", subtitle = "Process Memomry", xlab = "Month" , ylab = "Allocated server process(MB)"))


qicharts2::qic(x = mydate, y = Process_Memory, data = data, chart = "s", subtitle = "Process Memomry", xlab = "Month" , freeze =20 , ylab = "Allocated server process(MB)")

summary(qicharts2::qic(x = mydate, y = Process_Memory, data = data, chart = "s", subtitle = "Process Memomry", xlab = "Month" , freeze =20 , ylab = "Allocated server process(MB)"))


```



#Process Memory  Run chart


```{r}

qicharts2::qic(x = mydate, y = Process_Memory, data = data, chart = "run", subtitle = "Process Memory",xlab = "Month", ylab = "Allocated server process(MB)")
summary(qicharts2::qic(x = mydate, y = Process_Memory, data = data, chart = "run", subtitle = "Process Memory",xlab = "Month", ylab = "Allocated server process(MB)"))

qicharts2::qic(x = mydate, y = Process_Memory, data = data, chart = "run", subtitle = "Process Memory",xlab = "Month", freeze = 20 , ylab = "Allocated server process(MB)")

summary(qicharts2::qic(x = mydate, y = Process_Memory, data = data, chart = "run", subtitle = "Process Memory",xlab = "Month", freeze =20 ,ylab = "Allocated server process(MB)"))


```


#Prediction - the value predicted by the model

Is the prediction time of the model in control? "No" it's out of control as we could observe the red dott out of the lower and upper control limits.



#Prediction Xbar Chart


```{r}
qicharts2::qic(x = mydate, y = Prediction, data = data, chart = "xbar", subtitle = "Prediction", xlab = "Month" , ylab = "Prediction by Model (MB)")

summary(qicharts2::qic(x = mydate, y = Prediction, data = data, chart = "xbar", subtitle = "Prediction", xlab = "Month" , ylab = "Prediction by Model (MB)"))


qicharts2::qic(x = mydate, y = Prediction, data = data, chart = "xbar", subtitle = "Prediction", xlab = "Month" , freeze = 20 , ylab = "Prediction by Model (MB)")

summary(qicharts2::qic(x = mydate, y = Prediction, data = data, chart = "xbar", subtitle = "Prediction", xlab = "Month" , freeze = 20 , ylab = "Prediction by Model (MB)"))

```



#Prediction S Chart


```{r}
qicharts2::qic(x = mydate, y = Prediction, data = data, chart = "s", subtitle = "Prediction", xlab = "Month" , ylab = "Prediction by Model (MB)")

summary(qicharts2::qic(x = mydate, y = Prediction, data = data, chart = "s", subtitle = "Prediction", xlab = "Month" , ylab = "Prediction by Model (MB)"))
qicharts2::qic(x = mydate, y = Prediction, data = data, chart = "s", subtitle = "Prediction", xlab = "Month", freeze = 20 , ylab = "Prediction by Model (MB)")

summary(qicharts2::qic(x = mydate, y = Prediction, data = data, chart = "s", subtitle = "Prediction", xlab = "Month", freeze = 20 , ylab = "Prediction by Model (MB)"))

```


#Prediction Run Chart


```{r}

qicharts2::qic(x = mydate, y = Prediction, data = data, chart = "run",  subtitle = "Prediction", xlab = "Month" , ylab = "Prediction by Model (MB)")

summary(qicharts2::qic(x = mydate, y = Prediction, data = data, chart = "run",  subtitle = "Prediction", xlab = "Month" , ylab = "Prediction by Model (MB)"))

qicharts2::qic(x = mydate, y = Prediction, data = data, chart = "run", freeze = 20, subtitle = "Prediction- Freeze Limit 20", xlab = "Month" , ylab = "Prediction by Model (MB)")

summary(qicharts2::qic(x = mydate, y = Prediction, data = data, chart = "run", freeze = 20, subtitle = "Prediction", xlab = "Month" , ylab = "Prediction by Model (MB)"))

```



#PredictionTimeMS - the duration of the prediction task in milliseconds

 Is the prediction time of the model in control? No it's out of control ones the freezed parameter been applied, we get 4-5 outofcontrol values.Hence its Not in control.



#Prediction Time MS  X bar chart


```{r}
qicharts2::qic(x = mydate, y = prediction_timems, data = data, chart = "xbar",subtitle = "Prediction Time", xlab ="Month", ylab = "Prediction task in milliseconds" )

summary(qicharts2::qic(x = mydate, y = prediction_timems, data = data, chart = "xbar", subtitle = "Prediction Time", xlab ="Month", ylab = "Prediction task in milliseconds" ))


qicharts2::qic(x = mydate, y = prediction_timems, data = data, chart = "xbar",freeze = 20 ,subtitle = "Prediction Time", xlab ="Month", ylab = "Prediction task in milliseconds" )

summary(qicharts2::qic(x = mydate, y = prediction_timems, data = data, chart = "xbar", freeze = 20, subtitle = "Prediction Time", xlab ="Month", ylab = "Prediction task in milliseconds" ))

```


#Prediction Time MS  S bar chart

```{r}


qicharts2::qic(x = mydate, y = prediction_timems, data = data, chart = "s", subtitle = "Prediction Time", xlab ="Month", ylab = "Prediction task in milliseconds")
summary(qicharts2::qic(x = mydate, y = prediction_timems, data = data, chart = "s", subtitle = "Prediction Time", xlab ="Month", ylab = "Prediction task in milliseconds"))

qicharts2::qic(x = mydate, y = prediction_timems, data = data, chart = "s",freeze = 20,subtitle = "Prediction Time", xlab ="Month", ylab = "Prediction task in milliseconds")


summary(qicharts2::qic(x = mydate, y = prediction_timems, data = data, chart = "s", subtitle = "Prediction Time", xlab ="Month", freeze = 20 , ylab = "Prediction task in milliseconds"))

```



#Prediction Time MS  Run chart

```{r}

qicharts2::qic(x = mydate, y = prediction_timems, data = data, chart = "run", subtitle = "Prediction Time", xlab ="Month" , ylab = "Prediction task in milliseconds")

summary(qicharts2::qic(x = mydate, y = prediction_timems, data = data, chart = "run", subtitle = "Prediction Time", xlab ="Month", ylab = "Prediction task in milliseconds"))

qicharts2::qic(x = mydate, y = prediction_timems, data = data, chart = "run", subtitle = "Prediction Time", xlab ="Month" , freeze = 20 , ylab = "Prediction task in milliseconds")

summary(qicharts2::qic(x = mydate, y = prediction_timems, data = data, chart = "run", subtitle = "Prediction Time", xlab ="Month",freeze = 20, ylab = "Prediction task in milliseconds"))
```



